Measurement and Probability in Fuzzy Quantum Theories

### 2016-11-29 proposal/prop.tex
prop.tex \subsection{Proposed Activity I: Quantum States as Interactive Processes} Add citations...

\paragraph*{Research Question.} Does the computational and hence
\emph{testable} hypothesis that the quantum state is nothing but an
interactive system agree with the QBism perspective providing a
resolution to the same paradoxes (e.g., EPR and Wigner's friend)?

>>>>

\paragraph*{Research Question.} Does the computational and hence
\emph{testable} hypothesis that the quantum state is nothing but an
interactive system agree with the QBism perspective providing a
resolution to the same paradoxes (e.g., EPR~\cite{EPR1935} and Wigner's
friend~\cite{Wigner1961,Fuchs2010,Fuchs2012})?
